Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-04 src/tex/ms.tex
Add appendix plots

>>>>

\section{Extended corner plot for GW190521}
\label{sec:corner_GW190521_appendix}

\begin{figure*}[h]
    \script{corner_GW190521_appendix.py}
    \includegraphics[width=\textwidth]{figures/corner_GW190521_appendix.pdf}
    \caption{
        Extended corner plot for GW190521: a supplement to Fig.~\ref{fig:corner_GW190521} discussed in Appendix~\ref{sec:corner_GW190521_appendix}.
    }
    \label{fig:corner_GW190521_appendix}
\end{figure*}

\section{Extended corner plot for GW191105}
\label{sec:corner_GW191105_appendix}

\begin{figure*}[h]
    \script{corner_GW191105_appendix.py}
    \includegraphics[width=\textwidth]{figures/corner_GW191105_appendix.pdf}
    \caption{
        Extended corner plot for GW191105: a supplement to Fig.~\ref{fig:corner_GW191105} discussed in Appendix~\ref{sec:corner_GW191105_appendix}.
    }
    \label{fig:corner_GW191105_appendix}
\end{figure*}

\section{Extended corner plot for GW200129}
\label{sec:corner_GW200129_appendix}

\begin{figure*}[h]
    \script{corner_GW200129_appendix.py}
    \includegraphics[width=\textwidth]{figures/corner_GW200129_appendix.pdf}
    \caption{
        Extended corner plot for GW200129: a supplement to Fig.~\ref{fig:corner_GW200129} discussed in Appendix~\ref{sec:corner_GW200129_appendix}.
    }
    \label{fig:corner_GW200129_appendix}
\end{figure*}
